Presentation Plan\\ FF-Replan: \& RFF\@: Exploiting classical AI planning for uncertain and probabilistic domains

### 2014-02-23 presentation-plan/presentation-plan.tex
Adding theorems of the paper

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}

@@

The paper presents the Robust FF (\texttt{RFF}) planner, which should solve the
issues. \texttt{RFF} first generates an initial plan from the initial state to
some goal using \texttt{FF} on a determination of the MDP\@. Then for each
state in the plan, the successors of that state are added too. This is
expanding the execution structure. For the new state the probability to reach
this state should be higher than a certain threshold and if \texttt{FF} does
not return a failure for this state and a certain goal.

>>>>

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{fixltx2e}

@@

The paper presents the Robust FF (\texttt{RFF}) planner, which should solve the
issues. \texttt{RFF} first generates an initial plan from the initial state to
some goal using \texttt{FF} on a determination of the MDP\@. Then for each
state in the plan, the successors of that state are added too. This is
expanding the execution structure. For the new state the probability to reach
this state should be higher than a certain threshold and if \texttt{FF} does
not return a failure for this state and a certain goal. The calculation of the
probability to a state from the initial state can be costly. To optimize this
in \texttt{RFF} a Monte-Carlo (MC) simulation is used. \texttt{RFF} terminates
if either the global probability is lower than the threshold, or there are no
new terminal states to be added.

Three theorems, one lemma and one corollary about MDP problems using
\texttt{RFF} are given:

\begin{description}
	\item[Lemma 1] For every MDP planning problem RFF terminates in
		finite time
	\item[Theorem 1] (Soundness of \texttt{RFF\textsubscript{MPO}}). For every
		MDP planning problem, every solution that
		\texttt{RFF\textsubscript{MPO}} finds is correct
	\item[Theorem 2] (Completeness of \texttt{RFF\textsubscript{AO}}). For
		every MDP planning problem, if a solution exists, it is found by
		\texttt{RFF\textsubscript{AO}} or returns a failure
	\item[Corollary 1] (Soundness of \texttt{RFF\textsubscript{AO}}). For every
		MDP planning problem, every solution that
		\texttt{RFF\textsubscript{AO}} finds is correct
	\item[Theorem 3] If there are no unsolvable states in the MDP, then the
		probability of success of any solution found by \texttt{RFF} is
		higher than $1 - \rho$ where $\rho$ is the threshold probability
\end{description}
